---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# basicPLS

The objective of basicPLS is to provide a reduced implementation of PLS-SEM. The 
package is currently intentionally incomplete, as we are only implementing the
features we need. The implementation follows that found in [plspm](https://github.com/gastonstat/plspm). 

The main function is `basicPLS::PLS` and fits PLS-SEM with formative 
and pseudo-reflective measurement models (pseudo-reflective because PLS-SEM always
fits a formative model).

## Example:

```{r, message=FALSE}
library(basicPLS)
data_set <- basicPLS::satisfaction

# Both, measurement and structural model are specified using R's formulas:
PLS_result <- PLS(
  measurement = alist(EXPE ~ expe1 + expe2 + expe3 + expe4 + expe5,
                      IMAG ~ imag1 + imag2 + imag3 + imag4 + imag5,
                      LOY ~ loy1 + loy2 + loy3 + loy4,
                      QUAL ~ qual1 + qual2 + qual3 + qual4 + qual5,
                      SAT ~ sat1 + sat2 + sat3 + sat4,
                      VAL ~ val1 + val2 + val3 + val4),
  structure = alist(QUAL ~ EXPE,
                    EXPE ~ IMAG,
                    SAT ~ IMAG + EXPE + QUAL + VAL,
                    LOY ~ IMAG + SAT,
                    VAL ~ EXPE + QUAL),
  data = data_set)
PLS_result

# Use confidence_intervals to bootstrap confidence intervals for all parameters:
ci <- confidence_intervals(PLS_result,
                           # increase for actual use:
                           R = 50)
ci$confidence_intervals$effects
```

To switch to mode_A ("reflective") for a composite, use `as_reflective`:

```{r}
PLS_result <- PLS(
  measurement = alist(EXPE ~ expe1 + expe2 + expe3 + expe4 + expe5,
                      IMAG ~ imag1 + imag2 + imag3 + imag4 + imag5,
                      LOY ~ loy1 + loy2 + loy3 + loy4,
                      QUAL ~ qual1 + qual2 + qual3 + qual4 + qual5,
                      SAT ~ sat1 + sat2 + sat3 + sat4,
                      VAL ~ val1 + val2 + val3 + val4),
  structure = alist(QUAL ~ EXPE,
                    EXPE ~ IMAG,
                    SAT ~ IMAG + EXPE + QUAL + VAL,
                    LOY ~ IMAG + SAT,
                    VAL ~ EXPE + QUAL),
  as_reflective = c("EXPE", "IMAG", "LOY", "QUAL", "SAT", "VAL"),
  data = data_set)
PLS_result
```


## Weighted PLS

basicPLS can compute weighted PLS estimates:

```{r}
# data set with missings:
data_set <- basicPLS::satisfaction_NA

PLS_result <- PLS(
  measurement = alist(EXPE ~ expe1 + expe2 + expe3 + expe4 + expe5,
                      IMAG ~ imag1 + imag2 + imag3 + imag4 + imag5,
                      LOY ~ loy1 + loy2 + loy3 + loy4,
                      QUAL ~ qual1 + qual2 + qual3 + qual4 + qual5,
                      SAT ~ sat1 + sat2 + sat3 + sat4,
                      VAL ~ val1 + val2 + val3 + val4),
  structure = alist(QUAL ~ EXPE,
                    EXPE ~ IMAG,
                    SAT ~ IMAG + EXPE + QUAL + VAL,
                    LOY ~ IMAG + SAT,
                    VAL ~ EXPE + QUAL),
  data = data_set,
  # specify missing value treatment:
  imputation_function = mean_impute,
  # specify sample weights:
  sample_weights = data_set$sample_weights
  )
PLS_result

get_r2(PLS_result)
```
