---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# basicPLS

> basicPLS should not be used for any relevant data analysis; We recommend cSEM instead.

The objective of basicPLS is to provide a simple implementation of PLS-SEM to
better understand the algorithm underlying the modeling approach. The implementation
follows that found in [plspm](https://github.com/gastonstat/plspm). 

The main function is `basicPLS::PLS` and fits PLS-SEM with formative measurement
models.

## Example:

```{r, message=FALSE}
library(cSEM)
library(basicPLS)
data_set <- 10*cSEM::threecommonfactors + 2
PLS_result <- PLS(measurement = alist(eta1 ~ y11 + y12 + y13,
                                      eta2 ~ y21 + y22 + y23,
                                      eta3 ~ y31 + y32 + y33),
                  structure = alist(eta2 ~ eta1,
                                    eta3 ~ eta1 + eta2),
                  data = data_set)
PLS_result

# same thing with cSEM
model <- "
# Structural model
eta2 ~ eta1
eta3 ~ eta1 + eta2

# measurement model
eta1 <~ y11 + y12 + y13
eta2 <~ y21 + y22 + y23
eta3 <~ y31 + y32 + y33
"
fit_csem <- csem(data_set,
                 model,
                 .PLS_modes = "modeB")

# Let's compare the results:
fit_csem$Estimates$Weight_estimates
PLS_result$weights

fit_csem$Estimates$Path_estimates
PLS_result$effects

head(fit_csem$Estimates$Construct_scores -
       PLS_result$components)

assess(fit_csem, "r2")
get_r2(PLS_result)
```

